---
output:
  word_document: 
    toc: true
  html_document: default
---
Installing required packages

```{r}
if (!require("pacman")|!require("groundhog")| !require("here")) {
  
  install.packages(c("pacman","groundhog", "here"))
}


library("pacman")
library("here")
library("groundhog")
```

install.packages("groundhog")

```{r}
library("groundhog")
set.groundhog.folder(here("groundhog_library"))
groundhog.day = "2024-04-25" #'"2020-05-12"
```

Dowloaded fromn https://github.com/CredibilityLab/groundhog

```{r}
pkgs = c("dplyr", "tidyverse", "janitor", "sf"
         , "tmap", "devtools", "renv", "Hmisc", "ggplot2"
         , "xfun", "remotes", "sp", "spdep", "maptools"
         , "foreach", "doParallel", "parallel", "progress"
         , "doSNOW", "purrr", "patchwork", "rmapshaper"
         , "dplyr", "openxlsx", "MASS", "reticulate"
         , "future", "furrr", "data.table","leaflet"
         , "spgwr"
         )
```

```{r}
groundhog.library(pkgs, groundhog.day)
library(parallel) # Core package, so no install

packageVersion("openxlsx")
```
```{r setup, include =  FALSE}

library(knitr)
opts_chunk$set(cache = TRUE)

```
Get LSOA boundaries:----
from: https://data.london.gov.uk/dataset/statistical-gis-boundary-files-london
dir.create(here("Data", "London"), showWarnings = FALSE)

```{r}
download.file("https://data.london.gov.uk/download/statistical-gis-boundary-files-london/9ba8c833-6370-4b11-abdc-314aa020d5e0/statistical-gis-boundaries-london.zip"
              , "london_boundaries.zip")
  
  unzip("london_boundaries.zip", exdir = here("Data", "London")
        , overwrite = TRUE
        , junkpaths = TRUE #' remove the defauklt path from the zip file
        )
  
london <- read_sf(here("Data", "London","LSOA_2011_London_gen_MHW.shp"))

plot(st_geometry(london))
london

london <- st_transform(london, crs = 4326)
```

Simplify shapes

```{r}
london2 <- ms_simplify(london)

neighb <- spdep::poly2nb( london2
                         , queen=TRUE
                       #' , snap=eps
)

coords <- st_coordinates(st_centroid(st_geometry(london2)))

plot(neighb, coords, col="grey", add = FALSE)
```

Get additional data compatible with LSOA boundaries:----
from: https://www.data.gov.uk/dataset/ffd9f142-6b70-412e-ab30-6442ff37f685/lsoa-atlas

```{r}
download.file("https://data.london.gov.uk/download/lsoa-atlas/0193f884-2ccd-49c2-968e-28aa3b1c480d/lsoa-data.csv"
              , destfile = here("Data"
                                , "London"
                                , "LSOA_Atlas.csv")
              )
```

Read the file

```{r}
lsoa_data <- read.csv(here("Data"
                             , "London"
                             , "LSOA_Atlas.csv")
                      , header = TRUE
                      , check.names = FALSE #' Col.names with numerals
                      ) %>% 
            dplyr::rename_at(1, ~'LSOA11CD')

lsoa_data[rowSums(is.na(lsoa_data)) != ncol(lsoa_data), ]
```

Visual inspection of the data shows that the last two rows are not useful

```{r}
lsoa_data <- lsoa_data[1:(nrow(lsoa_data) - 2), ]
data.table::setDT(lsoa_data)
nrow(lsoa_data)
```

[1] 4835
Cleaning names

```{r}
lsoa_data <- clean_names(lsoa_data) %>% 
  dplyr::rename_at(1, ~'LSOA11CD')

colnames(lsoa_data)
```

Merge the data with the LSOA boundaries: ----

```{r}
lsoa_data_sf <- merge(london2, lsoa_data, by.x = "LSOA11CD", by.y = "LSOA11CD")

table(duplicated(lsoa_data_sf$LSOA11CD))

lsoa_nbs <- spdep::poly2nb(lsoa_data_sf)

no_neighbors <- vapply(lsoa_nbs, function(x) identical(x, 0L), logical(1))
table(no_neighbors)
```

restrict to connected map

```{r}
lsoa_data_sf <- lsoa_data_sf[!no_neighbors,]
plot(st_geometry(lsoa_data_sf))
```

Leaving relevant variables

```{r}
lsoa_data_sf <- lsoa_data_sf %>% 
  dplyr::select(  "LSOA11CD"
                , "POPDEN"
                , "names"
                , "mid_year_population_estimates_all_ages_2011"
                , "mid_year_population_estimates_aged_16_29_2011"
                , "mid_year_population_estimates_aged_30_44_2011"
                , "mid_year_population_estimates_aged_45_64_2011"
                , "mid_year_population_estimates_aged_65_2011"
                , "mid_year_population_estimates_working_age_2011"
                , "x2011_census_population_age_structure_all_ages"
                , "household_composition_couple_household_without_dependent_children_2011"
                , "household_composition_lone_parent_household_2011"
                , "country_of_birth_percent_not_united_kingdom_2011"
                , "ethnic_group_white_percent_2011"  
                , "ethnic_group_mixed_multiple_ethnic_groups_percent_2011"                                                                
                , "ethnic_group_asian_asian_british_percent_2011"                                                                         
                , "ethnic_group_black_african_caribbean_black_british_percent_2011"                                                       
                , "ethnic_group_other_ethnic_group_percent_2011"                                                                          
                , "ethnic_group_bame_percent_2011" 
                , "household_language_percent_of_households_where_no_people_aged_16_or_over_have_english_as_a_main_language_2011"
                , "tenure_private_rented_percent_2011"
                , "tenure_social_rented_percent_2011"
                , "tenure_owned_with_a_mortgage_or_loan_percent_2011"
                , "house_prices_median_price_2010"
                , "house_prices_median_price_2011"
                , "house_prices_median_price_2012"
                , "adults_in_employment_percent_of_households_with_no_adults_in_employment_with_dependent_children_2011"
                , "economic_activity_economically_active_total_2011"                                                                      
                , "economic_activity_economically_inactive_total_2011"                                                                    
                , "economic_activity_economically_active_employee_2011"                                                                   
                , "economic_activity_economically_active_self_employed_2011"                                                              
                , "economic_activity_economically_active_unemployed_2011"                                                                 
                , "economic_activity_economically_active_full_time_student_2011"
                , "economic_activity_unemployment_rate_2011"
                , "qualifications_percent_no_qualifications_2011"
                , "health_bad_or_very_bad_health_percent_2011"
                , "car_or_van_availability_no_cars_or_vans_in_household_percent_2011"
              )
```


```{r}
saveRDS(lsoa_data_sf, here("Data","London", "lsoa_data_sf.rds"))
```


Adding other sources of data, check NOMIS

```{r}
dir(here("Data", "London"), pattern = ".csv")
```

Adding other sources of data, check Kaagle
https://www.kaggle.com/datasets/dalreada/all-uk-active-companies-by-sic-and-geolocated
Set-up account: https://koderkow.github.io/kaggler/articles/kaggler.html
Copy JSON file
Place the kaggle.json file in the ~/.kaggle/ directory 
THEN py_run_string("import kaggle")
Python kaggle API

```{r}
kaggle <- import("kaggle")
```

Download all files in dataset [see fifference between '''_download_file and '''_download_files]

```{r}
kaggle$api$dataset_download_files("dalreada/all-uk-active-companies-by-sic-and-geolocated"
                                 , path = here("Data", "London")
                                 , unzip = TRUE
                                 )
```

Downloads 2 files: AllCompanies2.csv and SIC.csv
Read the files, clean and generate variables

```{r}
require(lubridate)

companies_data <- read.csv(here("Data"
                           , "London"
                           , "AllCompanies2.csv")
                      , header = TRUE
                      , check.names = FALSE
                      ) %>% 
                 janitor::clean_names(.) %>% 
                  mutate(sic = ifelse(sic == "None", NA, sic)) %>% 
                  mutate(sic = as.integer(sic)) %>% 
                  filter(sic != 99999) %>%
                  mutate(sic = sprintf("%05d", sic)) %>% 
                  mutate(incorporation_date = as.Date(incorporation_date, format = "%d/%m/%Y")) %>% 
                  mutate(firm_age = interval(incorporation_date, Sys.Date()) / years(1)) %>% 
                  mutate(firm_age = round(firm_age, 0))
```
```{r}
companies_data %>% 
  filter(sic == "None") %>% 
  nrow() #'[1] 2.5% with empty SIC

```  
A dormant company is a company that has already been through the company registration 
and incorporation process but it does not carry out business activities in a given 
period of time. SIC code 99999.

```{r}
sic_df <- read.csv(here("Data"
                          , "London"
                          , "SIC.csv")
                          , header = TRUE
                          , check.names = FALSE
                          ) %>% 
            janitor::clean_names(.) %>% 
            mutate(sic_code = as.character(sic_code)) %>%
            mutate(sic_code = sprintf("%05s", sic_code))
```

Merge the SIC data with the companies data

```{r}
companies_data <- companies_data %>% 
  left_join(sic_df, by = c("sic"="sic_code"))

dim(companies_data)
```

[1] 3546225       8
Check if all companies have Y:X pairs

```{r}
colnames(companies_data)
dim(companies_data)


companies_data %>% 
  filter(is.na(latitude) | is.na(longitude)) %>% 
  nrow()
```

Check if all companies have SIC

```{r}
companies_data %>% 
  filter(is.na(sic)) %>% 
  nrow()
```

Merge the data with the LSOA boundaries:
Convert csv to sf

```{r}
points_sf <- st_as_sf(companies_data
                      , coords = c("longitude", "latitude")
                      , crs = st_crs(lsoa_data_sf))

points_sf$points_id <- seq_len(nrow(points_sf))
lsoa_data_sf$polygon_id <- seq_len(nrow(lsoa_data_sf))
```

Set up parallel processing

```{r}
num_cores <- parallel::detectCores() - 1  #' Leave one core free for system processes
cl <- makeCluster(num_cores)
```

Export necessary packages and functions to the cluster

```{r include=FALSE}
clusterEvalQ(cl, {
  library(sf)
  library(dplyr)
})
```

Function to process chunks

```{r}
process_chunk <- function(chunk, polygons) {
  #' Use st_intersects for efficient spatial join
  intersects <- sf::st_intersects(chunk, polygons)
  
  #' Assign polygon IDs to points
  chunk$matched_polygon_id <- sapply(intersects, function(x) {
    if (length(x) > 0) polygons$polygon_id[x[1]] else NA
  })
  
  #' Join polygon attributes
  chunk <- left_join(chunk, 
                     as.data.frame(polygons) %>% select(-geometry),
                     by = c("matched_polygon_id" = "polygon_id"))
  
  return(chunk)
}
```

Main processing function
```{r}
spatial_join <- function(points_sf, lsoa_data_sf, chunk_size = 100000) {
  
  #' Ensure validity of polygons
  lsoa_data_sf <- st_make_valid(lsoa_data_sf)
  
  #' Split points into chunks
  point_list <- split(points_sf, ceiling(seq_len(nrow(points_sf))/chunk_size))
  
  #' Export large objects to the cluster workers
  clusterExport(cl, c("lsoa_data_sf", "process_chunk"))
  
  #' Process chunks in parallel
  results <- parLapply(cl, point_list, process_chunk, polygons = lsoa_data_sf)
  
  #' Combine results
  points_with_polygon <- do.call(rbind, results)
  
  return(points_with_polygon)
}
```

Check points_id and polygon_id are present

```{r}
if (!"points_id" %in% names(points_sf)) stop("points_sf must have a 'points_id' column")
if (!"polygon_id" %in% names(lsoa_data_sf)) stop("lsoa_data_sf must have a 'polygon_id' column")
```

Perform the efficient spatial join

```{r}
points_with_polygon <- spatial_join(points_sf, lsoa_data_sf)
```

Clean up and save

```{r}
stopCluster(cl)
gc()
```

Save the resulting dbs

```{r}
require(here)

saveRDS(points_with_polygon, here("Data","London", "points_with_polygon.rds"))
saveRDS(lsoa_data_sf, here("Data","London", "lsoa_data_sf.rds"))

```

Starting point with saved data ----


lsoa_data_sf <- readRDS(here("Data","London", "lsoa_data_sf.rds"))


Create a color palette for polygons

```{r}
pal <- colorFactor(palette = "viridis", domain = lsoa_data_sf$polygon_id)
```

Summary of the join results

```{r}
cat("Points assigned to polygons:", sum(!is.na(points_with_polygon$matched_polygon_id)), "\n")
cat("Points not assigned to any polygon:", sum(is.na(points_with_polygon$matched_polygon_id)), "\n")
```

#'CHECK!!!!!! Lots of points not assigned to any polygon!!!!
Census data https://www.nomisweb.co.uk/census/2011/bulk
Job density https://www.nomisweb.co.uk/datasets/jd
Query https://www.nomisweb.co.uk/query/select/getdatasetbytheme.asp?theme=75&subgrp=Local+Characteristics
https://webarchive.nationalarchives.gov.uk/ukgwa/20160105230903/http://www.ons.gov.uk/ons/guide-method/classifications/current-standard-classifications/standard-industrial-classification/index.html
https://npalomin.github.io/pnum/IDBR.html
Boundaries detection (Following Legewie, 2018) -----
library("matrixStats")

```{r}
require("scales")
require("spdep")

groundhog.library(c("tidycensus", "stargazer", "lintr",
                    "styler", "matrixStats"
                   )
                  ,groundhog.day
                  ,force.install = TRUE
)
```


Difference variables

```{r}
require(here)

lsoa_data_sf <- readRDS(here("Data","London", "lsoa_data_sf.rds"))
colnames(lsoa_data_sf)
```

[14] "ethnic_group_white_percent_2011"                                                                              
[15] "ethnic_group_mixed_multiple_ethnic_groups_percent_2011"                                                       
[16] "ethnic_group_asian_asian_british_percent_2011"                                                                
[17] "ethnic_group_black_african_caribbean_black_british_percent_2011"                                              
[18] "ethnic_group_other_ethnic_group_percent_2011"                                                                 
[19] "ethnic_group_bame_percent_2011" 

```{r}
new_names <- c("p_race_white"
               , "p_race_mixed"
               , "p_race_asian_brit"
               , "p_race_african_carib_black"
               , "p_race_bame"
              )

old_names <- c("ethnic_group_white_percent_2011"
                 , "ethnic_group_mixed_multiple_ethnic_groups_percent_2011"
                 , "ethnic_group_asian_asian_british_percent_2011"
                 , "ethnic_group_black_african_caribbean_black_british_percent_2011"
                 , "ethnic_group_bame_percent_2011"
              )   

lsoa_data_sf <- lsoa_data_sf %>% 
                dplyr::rename_with(~ new_names, all_of(old_names)) %>% 
                dplyr::mutate(across(all_of(new_names), ~ . / 100))

vars <- c("p_race_white"
          , "p_race_mixed"
          , "p_race_asian_brit"
          , "p_race_african_carib_black"
          , "p_race_bame"
        )

table(new_names)

saveRDS(lsoa_data_sf, here("Data","London", "lsoa_data_sf.rds"))
```

Verifying if proportion data is correct

```{r}
lsos_data_sf <- readRDS(here("Data","London", "lsoa_data_sf.rds"))

filtered_data <- lsoa_data_sf %>%
  dplyr::filter(if_any(all_of(vars), all_vars(. >= 1)))

#View(filtered_data[vars]) # Should be an empty table
rm(filtered_data)
```

#'sp do not support empty geometries

```{r}
sum(st_is_empty(lsoa_data_sf))
```

[1] 0
chi_ct <- chi_ct[!st_is_empty(chi_ct), ]
FUNCTION ERRORS!!!!!
[1]: error in evaluating the argument 'x' in selecting a method for function 
'addAttrToGeom': empty geometries are not supported by sp classes: conversion failed
'ORIGIN ERROR 1: sp do not support empty geometries
'SOLUTION ERROR 1: remove empty geometries
'LOCATION ERROR 1: function areal_wombling:25; function areal_wombling_bayesian:84;
'                function areal_wombling_bayesian:130
'
'[2]: `mutate_()` was deprecated in dplyr 0.7.0. Please use `mutate()` instead.
'ORIGIN ERROR 2: function deprecated
'SOLUTION ERROR 2: use mutate instead of mutate_
'LOCATION ERROR 2: function areal_wombling:49&51
'DOWNSTREAM ERROR DUE TO SOLUTION 2:  mutate() cannot handle formulas directly. 
'use rlang::eval_tidy() to evaluate the formulas within the data frame’s context.
'modify your code to evaluate the formulas in dots_blv and dots_bmv and return a vector
'
debug(areal_wombling)

Loading functions

```{r}
require(here)

source(here("BoundaryDetection.R"))
```

Running areal wombling
```{r}
require(sf)

  bdr <- areal_wombling(  lsoa_data_sf
                        , vars
                        , threshold = NA
                       ) 
  
#{NA}= fuzzy wombling, {0,1}= crips wombling
```

Mapping boundaries

```{r}
par(mfrow = c(1, 2), mar = c(0, 0, 0, 0))
```

Plot 1: Areal units with proportion African-American

```{r}
require(scales)

scale_color <- col_numeric(c("#F1EEF6", "#034E7B"), domain = c(0, 1))
plot(as(lsoa_data_sf, "Spatial"),
     col = scale_color(lsoa_data_sf$p_race_african_carib_black),
     lwd = 0.01, bor = "white"
)
vals <- quantile(lsoa_data_sf$p_race_african_carib_black, probs = c(0, 0.25, .5, 0.75, 1), na.rm = TRUE)
legend(-87.87, 41.73,
       legend = c("0%", "25%", "50%", "75%", "100%"),
       fill = scale_color(vals), cex = 0.8,
       box.lty = 0, border = "#00000000", title = "Percent Black", title.adj = 3.5
)
```

Plot 2: Boundaries

```{r}
plot(bdr, lwd = rescale(bdr$p_race_african_carib_black_blv, to = c(0.1, 1.25)))

#The spatial lines object does not include city boundaries. Let's add them

chi <- st_union(lsoa_data_sf)
plot(as(chi, "Spatial"), lwd = 0.8, add = TRUE)

#Legend showing the scale of boundary values

legend(-87.87, 41.73,
       legend = c("0.0", "0.25", "0.5", "0.75", "1.0"),
       lwd = rescale(c(0, 0.25, 0.5, 0.75, 1), to = c(0.1, 1.25)),
       cex = 0.8, box.lty = 0, border = "#'00000000",
       title = "Boundary Value", title.adj = 3.5
)

png(here("Figures","p_race_african_carib_black_blv.png"), width = 800, height = 600)

dev.off()
```

aggregate from line segments to block group level

```{r}
require(here)

lsoa_data_sf_blv <- bind_rows(
  group_by(bdr@data, i) %>%
    summarise_at(vars(ends_with("blv")), max, na.rm = TRUE),
  group_by(bdr@data, j) %>%
    summarise_at(vars(ends_with("blv")), max, na.rm = TRUE) %>% dplyr::rename(i = j)
) %>%
  group_by(i) %>%
  summarise_at(vars(ends_with("blv")), max, na.rm = TRUE) %>% 
  janitor::clean_names()

lsoa_data_sf <- bind_cols(lsoa_data_sf
                                     , dplyr::select(lsoa_data_sf_blv
                                     , -i)
                                    )

saveRDS(lsoa_data_sf_blv, here("Data", "lsoa_data_sf_blv.rds"))
```

compare the boundary values for spatial lines (border line segments) with the
boundary values for areal units.
for spatial lines (border line segments) with the boundary values for areal units.

```{r}
par(mfrow = c(1, 2), mar = c(0, 0, 0, 0))
```

Plot 1: Boundary values for border line segments

```{r}
(summary_data <- bdr@data %>%
  summarise(mean_value = mean(p_race_african_carib_black_blv)
            , min_value = min(p_race_african_carib_black_blv)
            , max_value = max(p_race_african_carib_black_blv)
          )
)
```

```{r}
# plot(bdr, lwd = rescale(bdr$p_race_african_carib_black_blv, to = c(0.1, 1.25)))
plot(bdr, lwd = rescale(bdr$p_race_african_carib_black_blv, to = c(0.1, 0.35)))
# plot(bdr, lwd = bdr$p_race_african_carib_black_blv)

chi <- st_union(lsoa_data_sf)

plot(as(chi, "Spatial"), lwd = 0.5, add = TRUE)
legend(-87.87, 41.73,
       legend = c("0.0", "0.25", "0.5", "0.75", "1.0"),
       lwd = rescale(c(0, 0.25, 0.5, 0.75, 1), to = c(0.1, 0.35)),
       #' lwd = rescale(c(0, 0.25, 0.5, 0.75, 1), to = c(0.1, 1.25)),
       cex = 0.8, box.lty = 0, border = "#'00000000",
       title = "Boundary Value", title.adj = 3.5
)

png(here("Figures","Boundary_values_segment.png"), width = 800, height = 600)
```

Plot 2: Boundary values for border line segments for areal units

```{r}
sel <- is.finite(lsoa_data_sf_blv$p_race_african_carib_black_blv)
scale_color <- col_numeric(c("#F1EEF6", "#034E7B"), domain = c(0, 1))
cols <- scale_color(lsoa_data_sf_blv$p_race_african_carib_black_blv[sel])

plot(as(lsoa_data_sf[sel, ], "Spatial"), lwd = 0.1, col = cols, bor = "white")
legend(-87.87, 41.73,
       legend = c("0.0", "0.25", "0.5", "0.75", "1.0"),
       fill = scale_color(c(0, 0.25, 0.5, 0.75, 1)), cex = 0.8, box.lty = 0,
       border = "#00000000", title = "Boundary Value", title.adj = 3.5
)

png(here("Figures","Boundary_values_areal.png"), width = 800, height = 600)
dev.off()
```

Spatial EDA -----
"r pkg("sfdep")" "Python pkg("PySal")"
Spatial autocorrelation
Spatial heterogeneity
Spatial regression -----

```{r}
new_names2 <- c("working_age_pop"
               , "all_ages_pop" #'CHECK!!!
               , "lone_parent_hh"
               , "not_uk_born"
               , "no_english_main_lang"
               , "house_price_2010"
               , "no_adults_in_employment"
               , "full_time_student"
               , "unemployment_rate"
               , "no_qualifications"
               , "bad_health"
              )

old_names2 <- c("mid_year_population_estimates_working_age_2011"
               , "x2011_census_population_age_structure_all_ages"
               , "household_composition_lone_parent_household_2011"
               , "country_of_birth_percent_not_united_kingdom_2011"
               , "household_language_percent_of_households_where_no_people_aged_16_or_over_have_english_as_a_main_language_2011"
               , "house_prices_median_price_2010"
               , "adults_in_employment_percent_of_households_with_no_adults_in_employment_with_dependent_children_2011"
               , "economic_activity_economically_active_full_time_student_2011"
               , "economic_activity_unemployment_rate_2011"
               , "qualifications_percent_no_qualifications_2011"
               , "health_bad_or_very_bad_health_percent_2011"
              )

lsoa_data_sf <- lsoa_data_sf %>% 
  dplyr::rename_with(~ new_names2, all_of(old_names2))
```

Create variable with count of companies, using matched id
Assuming that lsoa_data_sf$polygon_id matches points_with_polygon$matched_polygon_id
The coalesce() function at the end ensures that polygons with no matching points get a count of 0 instead of NA

Convert points_with_polygon to a regular data frame for counting

```{r}
library(sf)

points_df <- points_with_polygon %>%
  st_drop_geometry() %>%
  group_by(matched_polygon_id) %>%
  summarise(company_count = n())
```

Join count data to the sf object

```{r}
library(dplyr)

lsoa_data_sf <- readRDS(here("Data","London", "lsoa_data_sf.rds"))

lsoa_data_sf <- lsoa_data_sf %>%
  left_join(points_df, by = c("polygon_id" = "matched_polygon_id")) %>%
  mutate(company_count = coalesce(.$company_count, 0))  #' Replace NA with 0 for polygons with no points
```

Legewie (2018) derives two measures from the boundary values that are appropriate for multi-group settings. 
Change this as this is not correct

```{r}
require(here)

lsoa_data_sf <- readRDS(here("Data","London", "lsoa_data_sf.rds"))

lsoa_data_sf <- lsoa_data_sf %>%
  mutate(
    #' composite measure
    edge_wombling_race = matrixStats::rowMaxs(
      cbind(p_race_white_blv
            ,p_race_mixed_blv
            ,p_race_asian_brit_blv
            ,p_race_african_carib_black_blv
            ,p_race_bame_blv
            )
      , na.rm = FALSE
                                          ),
    #' pairwise boundary measures
     edge_race_wm    = p_race_white_blv * p_race_mixed_blv
    ,edge_race_wab   = p_race_white_blv * p_race_asian_brit_blv
    ,edge_race_wafc  = p_race_white_blv * p_race_african_carib_black_blv
    ,edge_race_wb    = p_race_white_blv * p_race_bame_blv
    ,edge_race_mab   = p_race_mixed_blv * p_race_asian_brit_blv
    ,edge_race_mafc  = p_race_mixed_blv * p_race_african_carib_black_blv
    ,edge_race_wb    = p_race_mixed_blv * p_race_bame_blv
    ,edge_race_abafc = p_race_asian_brit_blv * p_race_african_carib_black_blv
    ,edge_race_abb   = p_race_asian_brit_blv * p_race_bame_blv
    ,edge_race_afcb  = p_race_african_carib_black_blv * p_race_bame_blv
  )

# merge
lsoa_data_sf <- left_join(lsoa_data_sf, lsoa_data_sf_blv, by = "polygon_id")
```

Run regressions ----
See https://github.com/cran-task-views/Spatial/blob/main/Spatial.md
#' Basic regression

```{r}
f1 <- "company_count ~ edge_wombling_race + log(all_ages_pop) + p_race_white +
               p_race_mixed + p_race_asian_brit  + p_race_african_carib_black +
               p_race_bame + lone_parent_hh + not_uk_born + house_price_2010 + 
               bad_health + working_age_pop"
m1 <- glm.nb(f1, data = lsoa_data_sf)

stargazer(m1
          , type = "text"
          , no.space = TRUE
          , star.cutoffs = c(0.05, 0.01, 0.001)
          , out = here("Output", "regression_tablef1.txt")
          )
```

Compare the composite measure to the pairwise boundary measures

```{r}
f2 <- "company_count ~ edge_wombling_race +log(all_ages_pop) + p_race_white  + 
               p_race_mixed + p_race_asian_brit  + p_race_african_carib_black + 
               p_race_bame + lone_parent_hh + not_uk_born + house_price_2010 +  
               bad_health + working_age_pop"

f3 <- "company_count ~ edge_race_wm + edge_race_wab + edge_race_wafc + edge_race_wb +     
                          edge_race_mab + edge_race_mafc + edge_race_wb + edge_race_abafc + 
                          edge_race_abb + edge_race_afcb + log(all_ages_pop) +  
                          p_race_white + p_race_mixed + p_race_asian_brit +  
                          p_race_african_carib_black + p_race_bame +  
                          lone_parent_hh + not_uk_born + house_price_2010 +  
                          bad_health + working_age_pop"

m2 <- glm.nb(f2, data = lsoa_data_sf)
m3 <- glm.nb(f3, data = lsoa_data_sf)

stargazer(m2, m3
          , type = "text"
          , no.space = TRUE
          , star.cutoffs = c(0.05, 0.01, 0.001)
          , column.labels = c("Composite measure", "Pairwise boundaries")
          , out = here("Output", "regression_tablef2f3.txt")
          )
```

#' GWR or spatially varying coefficient (SVC) models?
CAVEAT:collinearity tends to be problematic in GWR models, See Comber et al. 2022
https://onlinelibrary.wiley.com/doi/10.1111/gean.12316
r pkg("varycoef") and r pkg("spBayes")
r pkg("gwrr") pkg("GWmodel") pkg("spgwr")
Also fastgwr https://github.com/Ziqi-Li/FastGWR in Python

```{r}
library(spgwr)
```

Fixed Bandwidth
find optimal kernel bandwidth using cross validation

```{r}
fbw <- gwr.sel(eq1, 
               data = utla_shp, 
               coords=cbind( long, lat),
               longlat = TRUE,
               adapt=FALSE, 
               gweight = gwr.Gauss, 
               verbose = FALSE)
```

view selected bandwidth

```{r}
fbw
```

fit a gwr based on fixed bandwidth

```{r}
fb_gwr <- gwr(eq1, 
              data = utla_shp,
              coords=cbind( long, lat),
              longlat = TRUE,
              bandwidth = fbw, 
              gweight = gwr.Gauss,
              hatmatrix=TRUE, 
              se.fit=TRUE)

fb_gwr
```

write gwr output into a data frame

```{r}
fb_gwr_out <- as.data.frame(fb_gwr$SDF)

utla_shp$fmb_localR2 <- fb_gwr_out$localR2
```

mapping results
Local R2

```{r}
map_fbgwr1 = tm_shape(utla_shp) +
  tm_fill(col = "fmb_localR2", title = legend_title, palette = magma(256), style = "cont") + #' add fill
  tm_borders(col = "white", lwd = .1)  + #' add borders
  tm_compass(type = "arrow", position = c("right", "top") , size = 5) + #' add compass
  tm_scale_bar(breaks = c(0,1,2), text.size = 0.7, position =  c("center", "bottom")) + #' add scale bar
  tm_layout(bg.color = "white") #' change background colour
map_fbgwr1 + tm_shape(reg_shp) + #' add region boundaries
  tm_borders(col = "white", lwd = .5) #' add borders
legend_title = expression("Fixed: Local R2")
```

Adaptive bandwidth
find optimal kernel bandwidth using cross validation

```{r}
abw <- gwr.sel(eq1, 
               data = utla_shp, 
               coords=cbind( long, lat),
               longlat = TRUE,
               adapt = TRUE, 
               gweight = gwr.Gauss, 
               verbose = FALSE)
```

view selected bandwidth

```{r}
abw
```

Assessing model fit
write gwr output into a data frame

```{r}
ab_gwr_out <- as.data.frame(ab_gwr$SDF)

utla_shp$amb_ethnic <- ab_gwr_out$ethnic
utla_shp$amb_lt_illness <- ab_gwr_out$lt_illness
utla_shp$amb_localR2 <- ab_gwr_out$localR2
```

Mapping results
Local R2

```{r}
map_abgwr1 = tm_shape(utla_shp) +
  tm_fill(col = "amb_localR2", title = legend_title, palette = magma(256), style = "cont") + #' add fill
  tm_borders(col = "white", lwd = .1)  + #' add borders
  tm_compass(type = "arrow", position = c("right", "top") , size = 5) + #' add compass
  tm_scale_bar(breaks = c(0,1,2), text.size = 0.7, position =  c("center", "bottom")) + #' add scale bar
  tm_layout(bg.color = "white") #' change background colour
map_abgwr1 + tm_shape(reg_shp) + #' add region boundaries
  tm_borders(col = "white", lwd = .5) #' add borders
legend_title = expression("Adaptive: Local R2")
```

#' SGWR
See: https://github.com/Lessani252/SGWR
